An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-18 Tex/elsevier/trindade_appliedenergy_rev0.tex
reviewed CEGIS
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{However, in our variant CEGIS method proposed at this paper, there are four particular differences related to traditional CEGIS: (1) there is not test vectors and every candidate is generated during the run-time at the {\sc Synthesize} phase and sent to {\sc Verify} phase; (2) if the {\sc Verify} phase is not successful, then a new candidate is generated by {\sc Synthesize} and (3) the lower bound of {\sc Verify} phase is incremented in order to pursuit the lowest cost; (4) therefore, there is not the refinement from the {\sc Verify} back to {\sc Synthesize} phase (a new counterexample is not added to the {\sc inputs} set) because a FAIL during {\sc Verify} just discard the candidate, that can be feasible in the next iteration with a new lower bound.}

>>>>

However, in our variant CEGIS method proposed here, there are four particular differences related to the traditional CEGIS: 
(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard 
a given candidate that could be feasible in the next iteration with a new lower bound.
